Sentiment classification of online political discussions: a comparison of a word-based and dependency-based method

### 2014-03-21 manuscript.tex
PES last changes.

\author{Hugo Lewi Hammer \\
  Oslo and Akershus \\ University College \\ Department of Computer Science \\
  {\tt hugo.hammer@hioa.no} \\ \And
  Per Erik Solberg \\
   Spr\aa kbanken \\ The National Library \\ of Norway\\
  {\tt Per.Solberg@nb.no}\\ \And
  Lilja \O vrelid \\
   Department of Informatics \\ University of Oslo\\
  {\tt liljao@ifi.uio.no}}

@@

\subsection{Corpus postprocessing}
The sentiment corpus was PoS-tagged and parsed using the
Bohnet\&Nivre-parser \cite{Boh:Niv:12}. This parser is a
transition-based dependency parser with joint tagger that implements
global learning and a beam search for non-projective labeled
dependency parsing.  This latter parser has recently outperformed
pipeline systems (such as the Malt and MST parsers) both in terms of
tagging and parsing accuracy for typologically diverse languages such
as Chinese, English, and German. It has been reported to obtain a
labeled accuracy of 87.7 for Norwegian \cite{Sol14}.  The parser is
trained on the Norwegian Dependency Treebank (NDT). The NDT is a
treebank created at the National Library of Norway in the period
2011-2013, manually annotated with part-of-speech tags, morphological
features, syntactic functions and dependency graphs \cite{Sol14,Sol13}. It consists of approximately 600 000 tokens, equally
distributed between Norwegian Bokm{\aa}l and Nynorsk, the two Norwegian
written standards. Only the Bokm{\aa}l subcorpus has been used here. A
large proportion of the NDT is newspaper text, there are also
parliament transcripts, government reports and texts with a more
colloquial style from blogs. Detailed annotation guidelines in English
will be made available in April 2014 \cite{Kinn2013}.

>>>>

\author{Hugo Lewi Hammer \\
  Oslo and Akershus \\ University College \\ Department of Computer Science \\
  {\tt hugo.hammer@hioa.no} \\ \And
  Per Erik Solberg \\
   Spr\aa kbanken \\ The National Library \\ of Norway\\
  {\tt p.e.solberg@ifikk.uio.no}\\ \And
  Lilja \O vrelid \\
   Department of Informatics \\ University of Oslo\\
  {\tt liljao@ifi.uio.no}}

@@

\subsection{Corpus postprocessing}
The sentiment corpus was PoS-tagged and parsed using the
Bohnet\&Nivre-parser \cite{Boh:Niv:12}. This parser is a
transition-based dependency parser with joint tagger that implements
global learning and a beam search for non-projective labeled
dependency parsing.  This latter parser has recently outperformed
pipeline systems (such as the Malt and MST parsers) both in terms of
tagging and parsing accuracy for typologically diverse languages such
as Chinese, English, and German. It has been reported to obtain a
labeled accuracy of 87.7 for Norwegian \cite{Sol14}.  The parser is
trained on the Norwegian Dependency Treebank (NDT). The NDT is a
treebank created at the National Library of Norway in the period
2011-2013, manually annotated with part-of-speech tags, morphological
features, syntactic functions and dependency graphs \cite{Sol14,Sol13}. It consists of approximately 600 000 tokens, equally
distributed between Norwegian Bokm{\aa}l and Nynorsk, the two Norwegian
written standards. Only the Bokm{\aa}l subcorpus has been used here. Detailed annotation guidelines in English
will be made available in April 2014 \cite{Kinn2013}.
